Distributed Version Control Systems

### 2010-05-16 paper.tex
agregadas secciones de comparison: merging y sharing changes

If you work against a central repository, pulling and pushing do look very much like
the idea of checking out and checking in, but that's the only way of working in a centralized VCS.
In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
read-only mode (via ssh, http, or just sharing the directory) to let other people pull from them.

@@

@@

In case the number of developers is really big (for instance on an OpenSource project) then a single person cannot deal with the integration from all of them. Then a hierarchycal approach can be taken and there will be a level of integrators who are responsable for merging all the changes from a particular subsystem. A main integrator will merge all the changes from the subsystem's integrator to create and publish the public version.

>>>>

@@

\subsection{Merging}
Merging on Git between branches is greatly improved over SVN, because all the history of 
both branches is preserved over the merges. %agregar citation

\subsection{Sharing changes}
If you work simply pulling and pushing against a central repository, those operations do look 
very much like the operations idea of check out and check in in a centralized VCS, 
but that's the only way of sharing changes in a centralized VCS.
In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
read-only mode (via ssh, http, or simply sharing the directory) to let other people pull from them.

@@
